---
title: "tutorials"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tutorials}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## First we load the package
```{r setup}
library(linearmodel)
```

## The usage of the this package
This package is able to conduct **Single/Multiple linear regression** and provide some important statistics for the users. In addition, you can use the package to return some diagnosis plots which are used to check the potential assumption of the linear model. 

## How to use the package
There are five functions in the package and I will show you how they work by loading the dataset. ("mtcars") 

<<<<<<< HEAD
Load the dataset
=======
### load the dataset
>>>>>>> 66f881bdf5a132e3a18d253f809a195ba32b85c6
```{r}
data("mtcars")
X = cbind(mtcars$cyl, mtcars$hp, mtcars$drat, mtcars$wt)
Y = mtcars$mpg
```
<<<<<<< HEAD

Get the coefficients of the linear regression
```{r}
linear_model(X,Y)$coefficients
```

Get the residuals of the linear regression
```{r}
linear_model(X,Y)$residuals
```




```{r}
Independence(X,Y)
=======


```{r}
linear_model(X,Y)$coefficients
linear_model(X,Y)$residuals
>>>>>>> 66f881bdf5a132e3a18d253f809a195ba32b85c6
```


```{r}
<<<<<<< HEAD
=======
Linearity(X,Y)
```


```{r}
Independence(X,Y)
```


```{r}
>>>>>>> 66f881bdf5a132e3a18d253f809a195ba32b85c6
Cons_variance(X,Y)
```


```{r}
Normality(X,Y)
```


```{r}

```

```{r}

```

<<<<<<< HEAD

## Check the effeciency of the function compared to lm() in base package
```{r}
library(bench)

benchmark_result1 = bench::mark(as.vector((linear_model(X,Y))$coefficients),
    as.vector(lm(formula = mpg ~ cyl + hp + drat + wt, data = mtcars)$coefficients))
print(benchmark_result1)
benchmark_result1$total_time
```

```{r}
xb = summary(lm(formula = mpg ~ cyl + hp + drat + wt, data = mtcars))
benchmark_result2 = bench::mark(as.vector((linear_model(X,Y))$R_square),
    as.vector(xb$r.squared))
print(benchmark_result2)
benchmark_result2$total_time
=======
```{r}

>>>>>>> 66f881bdf5a132e3a18d253f809a195ba32b85c6
```
