---
title: "tutorials"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tutorials}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## First we load the package
```{r setup}
library(linearmodel)
```

## The usage of the this package
This package is able to conduct **Single/Multiple linear regression** and provide some important statistics for the users. In addition, you can use the package to return some diagnosis plots which are used to check the potential assumption of the linear model. 

## How to use the package
There are five functions in the package and I will show you how they work by loading the dataset. ("mtcars") 


Load the dataset
```{r}
data("mtcars")
X = cbind(mtcars$hp, mtcars$wt)
Y = mtcars$mpg
```


The input you use is like:
* `X`: The predictors of variables (can be a vector or a matrix)
* `Y`: The outcome variable (should be a vector)


Return the coefficients of the linear regression
```{r}
linear_model(X,Y)$coefficients
```

Return the residuals of the linear regression
```{r}
linear_model(X,Y)$residuals
```

Return the SSE of the linear regression
```{r}
linear_model(X,Y)$SSE
```

Return the SSR of the linear regression
```{r}
linear_model(X,Y)$SSR
```

Return the MSE of the linear regression
```{r}
linear_model(X,Y)$MSE
```

Return the R squared of the linear regression
```{r}
linear_model(X,Y)$R_square
```

Return the adjusted R squared of the linear regression
```{r}
linear_model(X,Y)$R_square_adjusted
```

Return the t statistics of the linear regression
```{r}
linear_model(X,Y)$t_stat
```

Return the p value of t statistics of the linear regression
```{r}
linear_model(X,Y)$pt_value
```

Return the F statistics of the linear regression
```{r}
linear_model(X,Y)$F_stat
```

Return the p value of F statistics of the linear regression
```{r}
linear_model(X,Y)$pf_value
```

Plot the partial regression plots of each predictors 
```{r}
Linearity(X,Y)
```

Plot the autocorrelation figures of the residuals
```{r}
Independence(X,Y)
```

Plot the residuals versus fitted Y
```{r}
Cons_variance(X,Y)
```

Plot the histogram of residuals
```{r}
Normality(X,Y)
```


```{r}

```

```{r}

```


## Check the effeciency of the function compared to lm() in base package
```{r}
library(bench)

benchmark_result1 = bench::mark(as.vector((linear_model(X,Y))$coefficients),
    as.vector(lm(formula = mpg ~  hp +  wt, data = mtcars)$coefficients))
print(benchmark_result1)
benchmark_result1$total_time
```

```{r}
xb = summary(lm(formula = mpg ~ hp + wt, data = mtcars))
benchmark_result2 = bench::mark(as.vector((linear_model(X,Y))$R_square),
    as.vector(xb$r.squared))
print(benchmark_result2)
benchmark_result2$total_time
```

```{r}


```
